Injrury Outcomes - WHW matrices

### 2022-11-29 injury_tables.Rmd
Added active travel mode

@@

      td4[, 2] <- as.numeric(td4[,2])
      # Compute risk per bn km travelled
      td4[, 2] <- round((td4[,3] / ( td4[,2] * 365)) * 
                          1000000000, 4)

@@

# add counts but first divide by distance
baseline_counts_km <- left_join(baseline_counts_agg, true_distances, by = c('mode', 'city', 'scenario'))
baseline_counts_km$value <- round((baseline_counts_km$value /(baseline_counts_km$mode_distance * 365))*1000000000,4)

@@

@@

      el <- inner_join(el, td4, by = 'stage_mode')
    }

@@

# add counts but first divide by population
baseline_counts_pop <- left_join(baseline_counts_agg, pop_df, by = c('city'))
baseline_counts_pop$value <- round(baseline_counts_pop$value /baseline_counts_pop$model_population *  100000, 2)
baseline_counts_pop <- left_join(baseline_counts_pop, true_distances, by = c('city', 'mode','scenario'))

@@

      td4[, 2] <- as.numeric(td4[,2])
      # Compute risk per 100 million hours travelled
      td4[, 2] <- round((td4[,3] / ( td4[,2] * 365)) * 
                          100000000, 4)

@@

      # City's population
      pop <- sum(io[[city]]$demographic$population)
      # Compute travel time travelled per capita
      td6 <- td5
      td6[[paste0(var,"_risk")]] <- unlist(td4[2])
      td6[[paste0(var,"_percapita")]] <- td6[[var]] * 365 / pop
      names(td6)[3] <- paste(names(td6)[2], names(td6)[3], sep = "_")
      dd <- full_join(dd, td6, by = 'stage_mode')
    }

@@

@@

# add counts but first divide by duration
baseline_counts_dur <- left_join(baseline_counts_agg, duration, by = c('mode', 'city', 'scenario'))
baseline_counts_dur$value <- round((baseline_counts_dur$value /(baseline_counts_dur$mode_duration * 365))*100000000,4)
baseline_counts_dur <- left_join(baseline_counts_dur,true_distances, by = c('city', 'mode','scenario'))

>>>>

# combine active travel modes
active_travel <- whw_list %>% filter(cas_mode == 'cycle' | cas_mode == 'pedestrian')
active_travel <- active_travel %>% group_by(str_mode, measure, city, scenario, country, continent) %>% summarise(
                                  value = sum(value), mode_distance = sum(mode_distance), cas_mode ='active_travel')

@@

      td4[, 2] <- as.numeric(td4[,2])

      # add active travel mode
      # filter out pedestrian and cycle trips, calculate sum of counts and distances and add to existing data
      active_travel <- td4 %>% filter(stage_mode == 'pedestrian' | stage_mode == 'cycle')
      active_travel <- active_travel %>% group_by() %>% summarise(stage_mode = 'active_travel', 
                                                                  x = sum(active_travel[,2]),
                                                                  y = sum(active_travel[,3]))
      colnames(active_travel) <- colnames(td4)

      td4 <- rbind(td4, active_travel)

      td5 <- td4 # save copy for risk per population

      # Compute risk per bn km travelled
      td4[, 2] <- round((td4[,3] / ( td4[,2] * 365)) * 
                          1000000000, 4)

@@

# add baseline counts

# merge baseline count with distance
baseline_counts_km <- left_join(baseline_counts_agg, true_distances, by = c('mode', 'city', 'scenario'))

# add active travel 
active_travel <- baseline_counts_km %>% filter(mode == 'cycle' | mode == 'pedestrian')
active_travel <- active_travel %>% group_by(city, scenario, country, continent, measure, ) %>% summarise(
                                   value = sum(value), mode_distance = sum(mode_distance), mode ='active_travel')

baseline_counts_km <- rbind(baseline_counts_km, active_travel)

# calculate value per distance
baseline_counts_km$value <- round((baseline_counts_km$value /(baseline_counts_km$mode_distance * 365))*1000000000,4)

@@

       # add active travel mode
      # filter out pedestrian and cycle trips, calculate sum of counts and distances and add to existing data
      active_travel <- td4 %>% filter(stage_mode == 'pedestrian' | stage_mode == 'cycle')
      active_travel <- active_travel %>% group_by() %>% summarise(stage_mode = 'active_travel', 
                                                                  x = sum(active_travel[,2]))
      colnames(active_travel) <- colnames(td4)

      td4 <- rbind(td4, active_travel)

@@

      el <- full_join(el, td4, by = 'stage_mode')
    }

@@

# add counts but first divide by population
baseline_counts_pop <- left_join(baseline_counts_agg, pop_df, by = c('city'))

# add active travel 
active_travel <- baseline_counts_pop %>% filter(mode == 'cycle' | mode == 'pedestrian')
active_travel <- active_travel %>% group_by(city, scenario, country, continent, measure ) %>% summarise(
                                   value = sum(value), model_population = sum(model_population), 
                                   mode ='active_travel')

baseline_counts_pop <- rbind(baseline_counts_pop, active_travel)

baseline_counts_pop$value <- round(baseline_counts_pop$value /baseline_counts_pop$model_population *  100000, 2)
baseline_counts_pop <- left_join(baseline_counts_pop, true_distances, by = c('city', 'mode','scenario'))

@@

      td4[, 2] <- as.numeric(td4[,2])

      # add active travel mode
      # filter out pedestrian and cycle trips, calculate sum of counts and distances and add to existing data
      active_travel <- td4 %>% filter(stage_mode == 'pedestrian' | stage_mode == 'cycle')
      active_travel <- active_travel %>% group_by() %>% summarise(stage_mode = 'active_travel', 
                                                                  x = sum(active_travel[,2]),
                                                                  y = sum(active_travel[,3]))
      colnames(active_travel) <- colnames(td4)

      td4 <- rbind(td4, active_travel)

      # Compute risk per 100 million hours travelled
      td4[, 2] <- round((td4[,3] / ( td4[,2] * 365)) * 
                          100000000, 4)

@@

      el <- full_join(el, td4, by = c('stage_mode'))
    }

@@

    td <- el %>% dplyr::select(-contains('count'))
    names(td)[2:ncol(td)] <- paste(names(td)[2:ncol(td)], city, sep = "_")
    td$measure <- ifelse(is.na(pref), "mean", pref)

    if (length(city_df[["td"]][[city]]) == 3){
      overall_el[[city]] <- data.table::rbindlist(city_df[["td"]][[city]])
         }

@@

# add counts but first divide by duration
baseline_counts_dur <- left_join(baseline_counts_agg, duration, by = c('mode', 'city', 'scenario'))

# add active travel 
active_travel <- baseline_counts_dur %>% filter(mode == 'cycle' | mode == 'pedestrian')
active_travel <- active_travel %>% group_by(city, scenario, country, continent, measure ) %>% summarise(
                                   value = sum(value), mode_duration = sum(mode_duration), 
                                   mode ='active_travel')

baseline_counts_dur <- rbind(baseline_counts_dur, active_travel)

baseline_counts_dur$value <- round((baseline_counts_dur$value /(baseline_counts_dur$mode_duration * 365))*100000000,4)
baseline_counts_dur <- left_join(baseline_counts_dur,true_distances, by = c('city', 'mode','scenario'))
